Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-03-24 paper.tex
Added files via upload

\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ &  $0.3\,\RH^{(2)}$  &  $\RH^{(2)}$   \\
\hline
THERMAL QUANTITIES$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
TIMESCALES$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.29 & 0.36 & 0.52 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.29 & 0.36 & 0.51 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.29 & 0.37 & 0.49 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.10 & 0.09 \\
$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 44 \\
$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.16 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a.\\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and Synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\

>>>>

\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
THERMAL QUANTITIES$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
TIMESCALES$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_ec)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{pp}(P=100\,m_pc)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{coul}(P=\,m_ec)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a.\\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and Synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_e/m_p$ smaller).\\
